### 2019-06-03 README.rmd
Edits README.Rmd and CONTRIBUTE.md

This produces the minimal code detected from the script. It also
detects the package dependencies as well and provides them in the code
(`libs = TRUE`).

@@

If you would like to copy your code to the clipboard, you can do that
by not specifying a file path. You can now paste as needed to create a
simpler script.

@@

So far, we've been using "prosepctive" provenance generated from the
static code prior to execution. *Rclean* can also be used with
"retrospective" provenance, which is recorded during execution of a
script. To do so, we can pass the provenance to the `clean` function
via `options`:

@@

*Contributing*: if you would like to contribute, please read [[CONTRIBUTING.md]].

>>>>

This produces the minimal code detected from the script. It also
detects library dependencies and inserts them into the code (`libs =
TRUE`).

@@

If you would like to copy your code to your clipboard, you can do that
by not specifying a file path. You can now paste as needed to create a
simpler script.

@@

So far, we've been using "prosepective" provenance generated from the
static code prior to execution. *Rclean* can also be used with
"retrospective" provenance, which is recorded during execution of a
script. Using it facilitates more accurate code cleaning, We can pass
the provenance to the `clean` function via `options`:

@@

*Contributing*: if you would like to contribute, please read [[CONTRIBUTE.md]].
